A Topography of Climate Change Research

### 2017-11-08 pres/APSIS_17_11_09.tex
screenshots, pres

\title[Climate Topography]{A Topography of Climate Change Research}
\subtitle{}
\author{Max Callaghan}
\institute[MCC]{
	\includegraphics[height=1cm,width=2cm]{MCC_Logo_RZ_rgb.jpg}
	\,
	\includegraphics[height=1cm]{hertie_logo.png}
}

@@

\begin{columns}
	\begin{column}{0.5\linewidth}
		\begin{center}
		\includegraphics[width=0.6\linewidth]{syrcover.png}
		\end{center}
	\end{column}
	\begin{column}{0.5\linewidth}
	\begin{center}
		\begin{itemize}
			\item Climate Change is complicated
			\item The IPCC \textit{assess} the science on climate change
			\item These assessments should be comprehensive, credible and relevant
		\end{itemize}
	\end{center}
	\end{column}
	\end{columns}

@@

\begin{columns}
	\begin{column}{0.5\linewidth}
		\begin{center}
			\includegraphics[width=0.85\linewidth]{../plots/wos_scopus_docs_time.png}
\begin{figure}
	\includegraphics[width=0.85\linewidth]{merged_IPCC_spectral.png}
	\caption{Source: \citet{Minx2017} }
\end{figure}
		\end{center}
	\end{column}
	\begin{column}{0.5\linewidth}
		\begin{center}
			\begin{itemize}
				\item Comprehensive, credible and relevant assessments become
				more challenging as the literature grows
			\end{itemize}
		\begin{remark}[]
			To understand, and to aid, scientific assessments of climate change, we need to machine read the literature
		\end{remark}
		\end{center}
	\end{column}
\end{columns}

@@

\begin{columns}
	\begin{column}{0.5\linewidth}
		\begin{center}
			\includegraphics[width=0.85\linewidth]{../plots/network_wg_65.png}
		\end{center}
	\end{column}
	\begin{column}{0.5\linewidth}
		\begin{center}
			\begin{itemize}
				\item A network of comprehensible topics is generated with 100 topics
				\item Topics can be matched to the IPCC working group from which the majority of the topic documents are referenced in
				\item Topics from the same working group are \textbf{significantly} more likely to be correlated with each other than those which are not
			\end{itemize}
		\end{center}
	\end{column}
\end{columns}

@@

\begin{columns}
	\begin{column}{0.6\linewidth}
		\begin{center}
			\includegraphics[width=\linewidth]{../plots/hot_topics_65.png}
		\end{center}
	\end{column}
	\begin{column}{0.4\linewidth}
		\begin{center}
			\begin{itemize}
				\item Negative emissions related topics have shown strong growth in recent years
				\item As have topics on food security and cities
			\end{itemize}
		\end{center}
	\end{column}
\end{columns}

@@

\begin{frame}{Outlook}

\begin{figure}

\tiny

\begin{ganttchart}[
	y unit title=0.3cm,
	y unit chart=0.5cm,
	x unit= 0.2cm,
	vgrid,hgrid,
	vgrid={{dotted,dotted,black}},
	title height=1,
	%     title/.style={fill=none},
	title label font=\bfseries\scriptsize,
	%bar/.style={fill=blue},
	bar height=0.7,
	bar label font=\tiny,
	%   progress label text={},
	group right shift=0,
	group top shift=0.7,
	group height=.3,
	group peaks width={0.2},
	inline]{1}{42}
	\gantttitle{2017}{9}
	\gantttitle{2018}{12}
	\gantttitle{2019}{12}
	\gantttitle{2020}{9} \\
	\gantttitlelist{2,...,4}{3} \gantttitlelist{1,...,4}{3} \gantttitlelist{1,...,4}{3} \gantttitlelist{1,...,3}{3} \\
	\gantttitlelist{4,...,12}{1} \gantttitlelist{1,...,12}{1}
	%\gantttitlelist{J,F,M,A,M,J,J,A,S,O,N,D}{1}
	\gantttitlelist{1,...,12}{1} \gantttitlelist{1,...,9}{1}\\

	% HERTIE
	\ganttgroup[inline=false]{Hertie Courses}{6}{42} \\

	\ganttbar[inline=false, bar/.append style={fill=rd}]{Research Design}{6}{15} \\
	\ganttbar[inline=false, bar/.append style={fill=methods}]{Methods}{6}{15} \\
	\ganttbar[inline=false, bar/.append style={fill=skills}]{Skills}{6}{15} \\
	\ganttbar[inline=false, bar/.append style={fill=rc}]{Research Colloquium}{19}{42} \\

	% HERTIE
	\ganttgroup[inline=false]{Thesis Research}{1}{42} \\
	\ganttbar[inline=false, bar/.append style={fill=research}]{Knowledge Map}{1}{5} \\
	\ganttbar[inline=false, bar/.append style={fill=research}]{Pyramid}{6}{15} \\

	\ganttbar[inline=false, bar/.append style={fill=research}]{Knowledge Accumulation}{16}{27} \\

	\ganttbar[inline=false, bar/.append style={fill=research}]{Evidence in Policy}{19}{27} \\

	\ganttbar[inline=false, bar/.append style={fill=research}]{Envelope}{28}{33} \\

	\ganttbar[inline=false, bar/.append style={fill=research}]{Revisions/Contingency}{34}{42} \\

	%\ganttlinkedbar[inline=false]{Task 2}{3}{7} \ganttnewline
	%\ganttmilestone[inline=false]{Milestone}{7} \ganttnewline

\end{ganttchart}

\end{figure}

>>>>

\title[Climate Topography]{A Topography of Climate Change Research}
\subtitle{}
\author{Max Callaghan}
\institute[MCC]{
	\includegraphics[height=1cm,width=2cm]{MCC_Logo_RZ_rgb.jpg}
%	\,
%	\includegraphics[height=1cm]{hertie_logo.png}
}

@@

\begin{columns}
	\begin{column}{0.5\linewidth}
		\begin{center}
		\includegraphics[width=0.6\linewidth]{syrcover.png}
		\end{center}
	\end{column}
	\begin{column}{0.5\linewidth}
	\begin{center}
		\begin{itemize}
			\item To contribute evidence-based policy-making on climate change, the IPCC aims to \textit{comprehensively} assess  
			\item These assessments should be aim to balance legitimacy, credibility and relevance \citep{Cash2001}
		\end{itemize}
	\end{center}
	\end{column}
	\end{columns}

@@

\begin{columns}
	\begin{column}{0.5\linewidth}
		\begin{center}
%			\includegraphics[width=0.85\linewidth]{../plots/wos_scopus_docs_time.png}
\begin{figure}
	\includegraphics[width=0.85\linewidth]{merged_IPCC_spectral.png}
	\caption{Source: \citet{Minx2017l} }
\end{figure}
		\end{center}
	\end{column}
	\begin{column}{0.5\linewidth}
		\begin{center}
			\begin{itemize}
				\item Comprehensive, credible and relevant assessments become
				more challenging as the literature grows
			\end{itemize}
		\begin{remark}[]
			To understand, and to aid, scientific assessments of climate change, we need to machine read the literature
		\end{remark}
		\end{center}
	\end{column}
\end{columns}

@@

\begin{columns}
	\begin{column}{0.6\linewidth}
		\begin{center}
			\includegraphics[width=0.85\linewidth]{../plots/network_wg_372.PNG}
		\end{center}
	\end{column}
	\begin{column}{0.4\linewidth}
		\begin{center}
			\begin{itemize}
				\item A network of comprehensible topics is generated with 100 topics
				\item Topics can be matched to the IPCC working group from which the majority of the topic documents are referenced in
				\item Topics from the same working group are \textbf{significantly} more likely to be correlated with each other than those which are not
			\end{itemize}
		\end{center}
	\end{column}
\end{columns}

\begin{columns}
	\begin{column}{0.6\linewidth}
		\begin{center}
			\includegraphics[width=0.85\linewidth]{../plots/shares_10_372.PNG}

			\medskip

			\includegraphics[width=0.85\linewidth]{../plots/sustainability.PNG}
		\end{center}
	\end{column}
	\begin{column}{0.4\linewidth}
		\begin{center}
			\begin{itemize}
				\item In later assessment periods, the largest topic is on research priorities and sustainability
			\end{itemize}
		\end{center}
	\end{column}
\end{columns}

@@

\begin{columns}
	\begin{column}{0.6\linewidth}
		\begin{center}
			\includegraphics[width=\linewidth]{../plots/top_20_372.png}
		\end{center}
	\end{column}
	\begin{column}{0.4\linewidth}
		\begin{center}
			\begin{itemize}
				\item Negative emissions related topics have shown strong growth since the end of AR5
				\item As have topics on cities and extreme weather events
			\end{itemize}
		\end{center}
	\end{column}
\end{columns}

@@

%\begin{frame}{Outlook}
%
%\begin{figure}
%
%\tiny
%
%\begin{ganttchart}[
%	y unit title=0.3cm,
%	y unit chart=0.5cm,
%	x unit= 0.2cm,
%	vgrid,hgrid,
%	vgrid={{dotted,dotted,black}},
%	title height=1,
%	%     title/.style={fill=none},
%	title label font=\bfseries\scriptsize,
%	%bar/.style={fill=blue},
%	bar height=0.7,
%	bar label font=\tiny,
%	%   progress label text={},
%	group right shift=0,
%	group top shift=0.7,
%	group height=.3,
%	group peaks width={0.2},
%	inline]{1}{42}
%	\gantttitle{2017}{9}
%	\gantttitle{2018}{12}
%	\gantttitle{2019}{12}
%	\gantttitle{2020}{9} \\
%	\gantttitlelist{2,...,4}{3} \gantttitlelist{1,...,4}{3} \gantttitlelist{1,...,4}{3} \gantttitlelist{1,...,3}{3} \\
%	\gantttitlelist{4,...,12}{1} \gantttitlelist{1,...,12}{1}
%	%\gantttitlelist{J,F,M,A,M,J,J,A,S,O,N,D}{1}
%	\gantttitlelist{1,...,12}{1} \gantttitlelist{1,...,9}{1}\\
%	
%	% HERTIE
%	\ganttgroup[inline=false]{Hertie Courses}{6}{42} \\
%	
%	\ganttbar[inline=false, bar/.append style={fill=rd}]{Research Design}{6}{15} \\
%	\ganttbar[inline=false, bar/.append style={fill=methods}]{Methods}{6}{15} \\
%	\ganttbar[inline=false, bar/.append style={fill=skills}]{Skills}{6}{15} \\
%	\ganttbar[inline=false, bar/.append style={fill=rc}]{Research Colloquium}{19}{42} \\
%	
%	% HERTIE
%	\ganttgroup[inline=false]{Thesis Research}{1}{42} \\
%	\ganttbar[inline=false, bar/.append style={fill=research}]{Knowledge Map}{1}{5} \\
%	\ganttbar[inline=false, bar/.append style={fill=research}]{Pyramid}{6}{15} \\
%	
%	
%	\ganttbar[inline=false, bar/.append style={fill=research}]{Knowledge Accumulation}{16}{27} \\
%	
%	\ganttbar[inline=false, bar/.append style={fill=research}]{Evidence in Policy}{19}{27} \\
%	
%	\ganttbar[inline=false, bar/.append style={fill=research}]{Envelope}{28}{33} \\
%	
%	\ganttbar[inline=false, bar/.append style={fill=research}]{Revisions/Contingency}{34}{42} \\
%	
%	%\ganttlinkedbar[inline=false]{Task 2}{3}{7} \ganttnewline
%	%\ganttmilestone[inline=false]{Milestone}{7} \ganttnewline
%	
%	
%	
%\end{ganttchart} 
%
%\end{figure}
%
%\end{frame}
